Effect of quality-adjusted production function inputs

### 2015-05-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw

<<SR and R trajectory plot function>>=
residualsTrajGraph <- function(data){
  plot <- ggplot(data=data) + 
    geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
    facet_grid(Country ~ flavor) +
    xlab(expression(Delta*r)) +
    ylab(expression(Delta*lambda)) +
    xy_theme()
  return(plot)
}
@

We can test our hypothesis that quality-adjusting the factors of production
and including energy will reduce the Solow residual ($\lambda$)
and the fitting residuals ($r$) by plotting
$\Delta\lambda$ vs. $\Delta r$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda \equiv \lambda - \lambda_{Unadjusted, \, Without \, energy}
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_r}
  \Delta r \equiv r - r_{Unadjusted, \, Without \, energy}.
\end{equation}
%

<<Solow_residual_trajectories, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual trajectories for the Cobb-Douglas model.">>=
residualsTrajGraph(filter(traj.data, model=="CD"))
@

>>>>

<<SR and R trajectory plot function>>=
residualsTrajGraph <- function(data){
  plot <- ggplot(data=data) + 
    geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
#     geom_path(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
    facet_grid(Country ~ flavor) +
    xlab(expression(Delta*r)) +
    ylab(expression(Delta*lambda)) +
    xy_theme() + 
    theme(legend.title=element_blank())
  return(plot)
}
@

We can test our hypothesis that quality-adjusting the factors of production
and including energy will reduce the Solow residuals~($\lambda$)
and the fitting residuals~($r$) by plotting
$\Delta \lambda_i$ vs. $\Delta r_i$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_r}
  \Delta r_i \equiv \left| r_i \right| - \left| r_{i, \,Unadjusted, \, Without \, energy} \right|.
\end{equation}
%
If most of the points fall in the lower-left quadrant of a graph, 
we can conclude that both Solow residual~($\lambda$) and
fitting residual~($r$) have decreased due to either 
quality-adjustment of the factors of production or 
including energy.

Figure~\ref{fig:Solow_residual_trajectories_CD} indicates that
for the Cobb-Douglas model, 
neither 
quality-adjusting the factors of production
nor including energy 
consistently reduces
the Solow residual or the fitting residual.

<<Solow_residual_trajectories_CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the Cobb-Douglas model.">>=
residualsTrajGraph(filter(traj.data, model=="CD"))
@

We can also calculate the average values for $\Delta \lambda$ and $\Delta r$ 
as shown in Table~\ref{tab:traj.means.CD}.
%
<<Trajectory_Means_CD, results="asis">>=
xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
               caption="Average $\\Delta\\lambda$ and $\\lambda r$ for Cobb-Douglas models.",
               label="tab:traj.means.CD", 
               digits=6) %>% 
  print(., 
        caption.placement="top", 
        size="\\tiny", 
        include.rownames=FALSE, 
        math.style.negative=TRUE)
@
%
These results for the Cobb-Douglas model indicate that 
we should perform the same analysis for the CES model.
